
\section{Introduction}

\begin{frame}
    \frametitle{Background}
    \begin{itemize}
    	\item 1.23 million deer-vehicle collisions occurred in the U.S. between July 1, 2011 and June 30, 2012.
    	\item Cost more than \$4 billion in vehicle damage.
    	\item The average claim for deer-vehicle collisions between July 1, 2011 and June 30, 2012 was \$3,305.
    	\item The Insurance Institute for Highway Safety (IIHS) noted that deer-vehicle collisions in the U.S. cause about 200 fatalities annually.
    \end{itemize}
\end{frame}




\section{Population Biology}

\begin{frame}
    \frametitle{Deer Population}
    \begin{itemize}
    	\item Assumptions
		\begin{itemize}
    		\item Population is near carrying capacity.
    		\item The only predidation is human i.e. hunting and car fatalaties.
    		\item No migration.
    		\end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Logistic Equation with Harvest}
	\vspace{-1cm}
	\begin{eqnarray*}
		\frac{dx}{dt} &=& rx \left( 1-\frac{x}{f} \right) -hx
	\end{eqnarray*}
	\begin{itemize}
		\item $f$ - Carrying capacity
		\item $r$ - Growth rate
		\item $h$ - Harvest rate
	\end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Logistic Equation with Harvest}
	\vspace{-1cm}
	\begin{eqnarray*}
		\frac{dx}{dt} &=& rx \left( 1-\frac{x}{f} \right) -hx\\
		\frac{dx}{dt} &=& rx-\frac{rx^{2}}{f}-hx\\
		\frac{dx}{dt} &=& (r-h)x-\frac{rx^{2}}{f}\\
		\frac{dx}{dt} &=& (r-h)x \left(1-\frac{rx^{2}}{f(r-h)} \right)\\
		\frac{dx}{dt} &=& \tilde{r}x \left( 1-\frac{x}{\tilde{f}} \right)		
	\end{eqnarray*}
\end{frame}

\begin{frame}
    \frametitle{Athens County, Ohio}
	\begin{itemize}
		\item Carrying capacity is approximately 28,000
		\item Growth rate is 1.7
		\item Harvest Rate is 0.16
		\item (Schwabe, \emph{et al.}, 2000)
	\end{itemize}
\end{frame}






\section{Insurance}

\begin{frame}
    \frametitle{State Regulations and Bond Funds}
%%%%%%%%%%%%% How insurance companies work
	\begin{itemize}
		\item Low risk government bonds
		\item Premiums from customers
		%%%%% AREA WHERE YOU LIVE AKA DEER, driving record, age, type of car
		\item Claims based on accidents
	\end{itemize}
\end{frame}